Rising Gun Violence in Toronto: An Analysis of Shootings and Firearm Discharges

### 2024-09-27 paper/paper.qmd
Final version

# Introduction
We used R [@citeR] programming language to analyze the data and plot the graphs for this paper. The folder structure for this paper follows the startup folder created by [@rohan]. It is very helpful in keeping everything organized. I also referenced many of the examples and techniques provided by @alexander2023telling, which helped me understand how to visualize the data and communicate the findings effectively. We used `dplyr` [@citedplyr] to process and transform the dataset for this paper efficiently, which made it easier to filter, group, and summarize the data. In addition, the `tidyverse` [@citetidyverse] packages is essential for simplifying data cleaning and analysis.`styler` [@citestyler] used in arranging code style. These tools help to organize and present data efficiently. I also plotted the graphs with ggplot2 [@citeggplot2] and read the csv file with `here` [@citehere].

>>>>

# Introduction
We used R programming language [@citeR] to analyze the data and plot the graphs for this paper. The folder structure for this paper follows the startup folder created by [@rohan]. It is very helpful in keeping everything organized. I also referenced many of the examples and techniques provided by Telling Stories with Data [@alexander2023telling], which helped me understand how to visualize the data and communicate the findings effectively. We used `dplyr` [@citedplyr] to process and transform the dataset for this paper efficiently, which made it easier to filter, group, and summarize the data. In addition, the `tidyverse` [@citetidyverse] packages is essential for simplifying data cleaning and analysis.`styler` [@citestyler] used in arranging code style. These tools help to organize and present data efficiently. I also plotted the graphs with `ggplot2` [@citeggplot2] and read the csv file with `here` [@citehere].
